Enhancement of SDR in Thessaloniki

### 2024-08-24 GHI_enh_04_investigate.tex
Commit 2024-08-24 06:14
Commit 2024-08-24 11:08
Commit 2024-08-24 19:11

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-07-05}

@@

\begin{verbatim}
Warning: Removed 23 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-5}
\end{figure}

\begin{verbatim}
Warning: Removed 229 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 28216 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}

@@

\begin{verbatim}
Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

\caption{ - empty caption - }\label{fig:groups-9}
\end{figure}
\begin{figure}[H]

\caption{ - empty caption - }\label{fig:groups-10}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-11}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-14}
\end{figure}

@@

lmY: 0.062157 +/- 0.054182

@@

lmY: 0.053059 +/- 0.041079

@@

\begin{verbatim}
2024-07-05 09:30:57.8 athan@tyler GHI_enh_04_investigate.R 2.177551 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-08-24}

@@

\begin{verbatim}
Warning: Removed 32 rows containing missing values or values outside the scale range
(`geom_bar()`).
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-5}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}
\begin{figure}[H]

\begin{verbatim}
Warning: Removed 252 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 28187 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\caption{ - empty caption - }\label{fig:groups-9}
\end{figure}

\begin{verbatim}
Warning: Removed 252 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 28187 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\caption{ - empty caption - }\label{fig:groups-10}
\end{figure}

@@

\begin{verbatim}
Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

@@

\caption{ - empty caption - }\label{fig:groups-11}
\end{figure}

\begin{verbatim}
Warning: Removed 252 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 28187 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-14}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-15}

\caption{ - empty caption - }\label{fig:groups-15}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-16}

\caption{ - empty caption - }\label{fig:groups-16}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-17}

\caption{ - empty caption - }\label{fig:groups-17}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-18}

\caption{ - empty caption - }\label{fig:groups-18}
\end{figure}

@@

lmY: 0.029427 +/- 0.054286

@@

lmY: 0.03518 +/- 0.042507

@@

\begin{verbatim}
2024-08-24 16:09:38.1 athan@tyler GHI_enh_04_investigate.R 1.792265 mins
\end{verbatim}
